Dialect: A Compact Line Notation Based on SMILES

### 2022-03-24 manuscript.tex
Clarifies definition of DIME. closes #65

A molecular representation based solely on the valence bond model can yield artifacts resulting from \textit{delocalization induced molecular equality} (DIME). DIME occurs in a molecular graph when one or more equivalent representations exist, each one differing from the original only in the distribution of single and double bonds. DIME may be recognized as "resonance" or "aromaticity," but those terms are avoided here due to their ambiguity.\cite{randic:2018,kerber:2006}

>>>>

A molecular representation based solely on the valence bond model can yield artifacts resulting from \textit{delocalization induced molecular equality} (DIME). DIME occurs when a molecular graph exists in two or more equal forms, each differing from the others only through electron delocalization. Two molecular graphs are equal if they are isomorphic and a 1:1 mapping exists between the atoms and bonds in each graph. Electron delocalization results when the electrons of a valence bond representation can be distributed over more than one atom pair, between two or more atoms, or across some combination of atoms and bonds. DIME is similar to "resonance" or "aromaticity," but those terms are avoided here due to their ambiguity.\cite{randic:2018,kerber:2006}
